### 2024-07-31 conteudo/methods/methods.tex
add more initial eval
adjust methods

\subsection{Evaluation of the tool by the formal literature}

@@

\subsection{Evaluation of the tool by Empirical analyses}

@@

The number of code lines and components in the Linux kernel makes it impractical to analyze every 
code duplication. To limit our scope, we will analyze solely code duplications in the AMD Display 
driver. This limitation still does not reduce the code duplication to analyze. In our preliminary 
tool execution shown in Figure \ref{fig:relatory_ex}, there are over 20,000 lines of code 
duplications on the AMD Display driver with a similarity metric of 100\%.

@@

When we analyze the selected function pairs, we will empirically judge if they are duplications,
which means we are not going deeper as categorizing the duplications by code duplication type. 
We intend to collect the data on this empirical analysis and compare it to the formal literature 
method to understand if our tool detects duplicated functions and the difference it makes when 
varying the minimum similarity parameter of our tool.

>>>>

\section{Evaluation of the tool by the formal literature}

\label{sec:metbig}

@@

\section{Evaluation of the tool by Empirical analyses}

\label{sec:metemp}

@@

The number of code lines and components in the Linux kernel makes it impractical to analyze every 
code duplication. To limit our scope, we will analyze solely code duplications in the AMD Display 
driver. This limitation still does not reduce the code duplication to analyze, in our preliminary 
tool execution shown in Figure \ref{fig:relatory_ex}, there are over 20,000 lines of code 
duplications on the AMD Display driver with a similarity metric of 100\%.

@@

When we analyze the selected function pairs, we will empirically judge if they are duplications. 
We intend to collect the data on this empirical analysis and compare it to the formal literature 
method to understand if our tool detects duplicated functions and the difference it makes when 
varying the minimum similarity parameter of our tool.
